The Driving Forces of API Evolution

### 2015-06-02 thesis/paper.tex
review johns

\subsection{APIs} 
%what is an API
An API offers an interface through which developers can use to access functionality of a system. APIs can be seen as having three interacting layers; the interfaces, the implementation and additional functionality. Typically, the interfaces provide the definitions of functions and data structures while the implementation realises those interfaces. The additional functionality exists as a middle layer that provides utilities such as error handling, third party libraries and additional auxiliary features.
%we consider APIs to be systems because x y z \cite{761853,5733835}
Given that there is a combination of different interacting elements that does not only concern interfaces to implementations, we would argue that an API can be described as a system \cite{761853,5733835}.
%Introduce different layers of an API.
%Headers / Interfaces
%Implementation
%"Middle Layer"

>>>>

\subsection{APIs} 
%what is an API
An API offers an interface through which developers can access programmatic functionality. APIs can be seen as having three interacting layers; the public interface, the actual implementation of the functionality and an intersecting layer which provides utilities such as error handling, third party libraries and additional auxiliary features. Typically, the interfaces provide the definitions of functions and data structures while the implementation realises those interfaces.
%we consider APIs to be systems because x y z \cite{761853,5733835}
Given that there is a combination of different interacting elements that do not only concern interfaces to implementations, we would argue that an API can be described as a system \cite{761853,5733835}.
%Introduce different layers of an API.
%Headers / Interfaces
%Implementation
%"Middle Layer"
